Automated Topic Naming

### 2012-01-19 ese/ese.tex
- [X] MiGOD: So you had difficulty agreeing on labels.  Did it       actually make a difference to the results?  (ie not the labels       themselves but the rest of the work)

>>>>

Were our results harmed by low IRR scores? For MaxDB and MySQL since
each annotator (Neil or Abram) acted as the sole Oracle, the results
for either system still stand, but construct validity is harmed in
terms of did if an NFR actually meant the NFR that is being
evaluated. The measured empirical performance of each system still
stands, but the comparison between systems in terms of NFRs might be
harmed by low IRR scores.
